---
title: "QQPlot Simulation"
author: "Logan Crowl"
date: "2/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
devtools::install_github("aloy/scagnostics")
library(scagnostics)
library(plyr)
library(nortest)
```

#Additional scagnostic-type measures (work in progress)
```{r}
deviation.base <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((y2 - x2)^2)
  return(deviation)
}

deviation.add <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((y2 - x2)^2 + abs(x2))
  return(deviation)
}

deviation.addSq <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((y2 - x2)^2 + x2^2)
  return(deviation)
}

deviation.addLog <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((y2 - x2)^2 + log(x2^2 + 1))
  return(deviation)
}

deviation.mult <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((abs(x2)+1)*(y2 - x2)^2)
  return(deviation)
}

deviation.multSq <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((x2^2+1)*(y2 - x2)^2)
  return(deviation)
}

deviation.multLog <- function(x,y){
  data <- (y - mean(y))/sd(y)
  qqplot <- qqnorm(data, plot.it = F)
  x2 <- qqplot$x
  y2 <- qqplot$y
  deviation <- (1/length(y2))*sum((log(x2^2+1)+1)*(y2 - x2)^2)
  return(deviation)
}
```

Skew or Kurtosis

$$
\frac{1}{n}\sum_{i=1}^k (y_{i}-x_{i})^2
$$
$$
\frac{1}{n}\sum_{i=1}^k((y_{i}-x_{i})^2 + \mid x_{i} \mid)
$$

$$
\frac{1}{n}\sum_{i=1}^k((y_{i}-x_{i})^2 + x_{i}^2)
$$

$$
\frac{1}{n}\sum_{i=1}^k((x_{i}^2+1)(y_{i}-x_{i})^2)
$$


$$
\frac{1}{n}\sum_{i=1}^k((log(x_{i}^2+1) + 1)(y_{i}-x_{i})^2)
$$


We will generate QQplots from random data from normal distributions, t-distributions, exponential distributions, log normal distributions, and chi-squared distributions.  We try to match variability for normal, t, and exponential distributions by setting sd of normal and exponential distributions to sqrt(df/(df-2)), which is the standard deviation of the t-distribution.  We also simulate one QQPlot for a normal distribution for every non-normal QQplot in order to maintain a 50-50 ratio of signal to noise.

```{r}
DF <- c(3,4,5,6,7)
Ns <- c(20,30,40,50)


QQPlots <- vector(mode = "list")
info <- vector(mode = "list")

set.seed(1)
index = 1
for(i in 1:100){
  for(n in Ns) {
    for(df in DF){
      #normal
      for(i in 1:4){ 
        normdata <- rnorm(n, 0,sqrt(df/(df-2)))
        norm <- qqnorm(normdata, plot.it = F)
        QQPlots[[index]] <- list(ID = index,  x = norm$x , y = norm$y)
        info[[index]] <- list(ID = index, N = n, distribution = "Normal", mean = 0, sd = sqrt(df/(df-2)), df = NA)
        index = index + 1
      }
      
      #t-distribution
      tdata <- rt(n, df = df) 
      t <- qqnorm(tdata, plot.it = F)
      QQPlots[[index]] <- list(ID = index,  x = t$x , y = t$y)
      info[[index]] <- list(ID = index, N = n, distribution = "T", mean = 0, sd = sqrt(df/(df-2)), df = df)
      index = index + 1
      
      #Exponential 
      expdata <- rexp(n, rate = 1/(sqrt(df/(df-2))))
      exp <- qqnorm(expdata, plot.it= F)
      QQPlots[[index]] <- list(ID = index,  x = exp$x , y = exp$y)
      info[[index]] <- list(ID = index, N = n, distribution = "Exponential", mean = sqrt(df/(df-2)), sd = sqrt(df/(df-2)), df = NA)
      index = index + 1
      
      #logNormal
      logNormData <- rlnorm(n, sdlog = sqrt(log(0.5 + 0.5*sqrt(1 + 4*df/(df-2)))))
      logNorm <- qqnorm(logNormData, plot.it = F)
      QQPlots[[index]] <- list(ID = index,  x = logNorm$x , y = logNorm$y)
      info[[index]] <- list(ID = index, N = n, distribution = "Log-Normal", mean = exp(df/(2*(df-2))), sd = sqrt(df/(df-2)), df = NA)
      index = index + 1
      
      #Chi-Squared
      chisqData <- rchisq(n, df) 
      chisq <- qqnorm(chisqData, plot.it = F)
      QQPlots[[index]] <- list(ID = index,  x = chisq$x , y = chisq$y)
      info[[index]] <- list(ID = index, N = n, distribution = "Chi-Squared", mean = df, sd = sqrt(2*df), df = df)
      index = index + 1
    }
  }
}

```

Now, we will generate the scagnostics for the plots
```{r}
QQscagnostics <- vector(mode = "list")

index = 1
for (plot in QQPlots) {
  if (index%%100 == 0){print(index)}
  QQscagnostics[[index]] <- list(ID = index, 
                                 scagnostics = scagnostics(plot$x, plot$y)$s, 
                                 AD_pvalue = ad.test(plot$y)$p.value, 
                                 SW_pvalue = shapiro.test(plot$y)$p.value, 
                                 CVM_pvalue = cvm.test(plot$y)$p.value, 
                                 lillie_pvalue = lillie.test(plot$y)$p.value, 
                                 pearson_pvalue = pearson.test(plot$y)$p.value, 
                                 SF_pvalue = sf.test(plot$y)$p.value, 
                                 deviation.base = deviation.base(plot$x, plot$y), 
                                 deviation.add = deviation.add(plot$x, plot$y),
                                 deviation.addSq = deviation.addSq(plot$x, plot$y), 
                                 deviation.addLog = deviation.addLog(plot$x, plot$y),
                                 deviation.mult = deviation.mult(plot$x, plot$y),
                                 deviation.multSq = deviation.multSq(plot$x, plot$y),
                                 deviation.multLog = deviation.multLog(plot$x, plot$y)
                                 )
  index = index + 1
}
```

Turn the data from lists of lists in data frames
```{r}
info_df <- ldply(info, data.frame)
QQPlots_df <- ldply(QQPlots, data.frame)

QQscagnostics_df <- ldply(QQscagnostics, data.frame)
scag_num <- rep(seq(1:9), 16000)
QQscagnostics_df$scag_num <- scag_num
```

save the CSV
```{r}
write.csv(info_df, "simulation_data/QQPlots_info.csv")
write.csv(QQPlots_df, "simulation_data/QQplots.csv")
write.csv(QQscagnostics_df, "simulation_data/QQPlots_scagnostics.csv")
```
