---
title: "cleaning_responses"
author: "Sophie Gunn"
date: "April 22, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
responses <- read_csv('for_study/Carl_Responses1.csv')
experiment_scagnostics <- read_csv('for_study/experiment_scagnostics.csv')
setA1 <- responses[c(3:52),c(1:10, 23)]
setB1 <- responses[c(3:52),c(1:4, 11:16, 23)]
setAN <- responses[c(3:52),c(1:4, 17:19, 23)]
setBN <- responses[c(3:52),c(1:4, 20:23)]

setA1 <- na.omit(setA1)
setB1 <- na.omit(setB1)
setAN <- na.omit(setAN)
setBN <- na.omit(setBN)
```

setA1
```{r}
ac1 <- sum(setA1$`A-1-Q1` == 14)/26 #should be 14
ac2 <- sum(setA1$`A-1-Q2` == 2)/26  #should be 2
ac3 <- sum(setA1$`A-1-Q3` == 15)/26  #should be 15
ac4 <- sum(setA1$`A-1-Q4` == 14)/26  #should be 14
ac5 <- sum(setA1$`A-1-Q5` == 9)/26  #should be 9
ac6 <- sum(setA1$`A-1-Q6` == 8)/26  #should be 8

avgac <- (ac1 + ac2+ ac3 + ac4 + ac5 + ac6)/6
avgac #77%
```

set AN
accuracy <- num they got correct / number total plots that are signal 
1 - (plots they got correct)/ones that they chose
```{r}
sum(setAN$`A-N-Q1` ) #should be 14 and 17
setAN %>% select(`A-N-Q1`) %>% 
  mutate( points_a = as.numeric(str_detect(`A-N-Q1`, '14')) ) %>% 
  mutate( points_b = as.numeric(str_detect(`A-N-Q1`, '17')) ) %>% 
  mutate( acc = (points_a + points_b)/2 ) %>% 
  summarize(acc_tot = mean(acc)) #68

sum(setAN$`A-N-Q2` ) #should be 5, 7, 10, 11, 15
setAN %>% select(`A-N-Q2`) %>% 
  mutate( points_a = as.numeric(str_detect(`A-N-Q2`, '5,')) ) %>% 
  mutate( points_b = as.numeric(str_detect(`A-N-Q2`, '7')) ) %>% 
  mutate( points_c = as.numeric(str_detect(`A-N-Q2`, '10')) ) %>% 
  mutate( points_d = as.numeric(str_detect(`A-N-Q2`, '11')) ) %>% 
  mutate( points_e = as.numeric(str_detect(`A-N-Q2`, '15')) ) %>% 
  mutate( acc = (points_a + points_b + points_c + points_d + points_e)/5 ) %>%
  summarize(acc_tot = mean(acc)) #67.2

sum(setAN$`A-N-Q3` ) #should be 6 and 14
setAN %>% select(`A-N-Q3`) %>% 
  mutate( points_a = as.numeric(str_detect(`A-N-Q3`, '14')) ) %>% 
  mutate( points_b = as.numeric(str_detect(`A-N-Q3`, '6')) ) %>% 
  mutate( acc = (points_a + points_b)/2 ) %>% 
  summarize(acc_tot = mean(acc)) #62

#false positives
setAN %>% select(`A-N-Q1`) %>% 
  mutate( len = as.numeric(str_detect(`A-N-Q1`, ',')) + 1 ) %>%  
  mutate( points_a = as.numeric(str_detect(`A-N-Q1`, '14')) ) %>% 
  mutate( points_b = as.numeric(str_detect(`A-N-Q1`, '17')) ) %>% 
   mutate( false_pos = 1 - (points_a + points_b)/len ) %>% summarize(false_pos_tot = mean(false_pos)) #0.0800


sum(setAN$`A-N-Q2` ) #should be 5, 7, 10, 11, 15
setAN %>% select(`A-N-Q2`) %>% 
  mutate( len = as.numeric(str_count(`A-N-Q2`, ',')) + 1 ) %>%  
  mutate( points_a = as.numeric(str_detect(`A-N-Q2`, '5,')) ) %>% 
  mutate( points_b = as.numeric(str_detect(`A-N-Q2`, '7')) ) %>% 
  mutate( points_c = as.numeric(str_detect(`A-N-Q2`, '10')) ) %>% 
  mutate( points_d = as.numeric(str_detect(`A-N-Q2`, '11')) ) %>% 
  mutate( points_e = as.numeric(str_detect(`A-N-Q2`, '15')) ) %>% 
  mutate( false_pos = 1 - (points_a + points_b + points_c + points_d + points_e)/len )%>% 
  summarize(false_pos_tot = mean(false_pos)) #0.0233

sum(setAN$`A-N-Q3` ) #should be 6 and 14
setAN %>% select(`A-N-Q3`) %>% 
   mutate( len = as.numeric(str_count(`A-N-Q3`, ',')) + 1 ) %>%  
  mutate( points_a = as.numeric(str_detect(`A-N-Q3`, '14')) ) %>% 
  mutate( points_b = as.numeric(str_detect(`A-N-Q3`, '6')) ) %>% 
  mutate( false_pos = 1 - (points_a + points_b)/len ) %>% 
  summarize(false_pos_tot = mean(false_pos)) #0.270
```

setB1
```{r}
ac1 <- sum(setB1$`B-1-Q1` == 20)/24
ac2 <- sum(setB1$`B-1-Q2` == 1)/24
ac3 <- sum(setB1$`B-1-Q3` == 14)/24 
ac4 <- sum(setB1$`B-1-Q4` == 8)/24 
ac5 <- sum(setB1$`B-1-Q5` == 17)/24 
ac6 <- sum(setB1$`B-1-Q6` == 8)/24

avgac <- (ac1 + ac2+ ac3 + ac4 + ac5 + ac6)/6
avgac #84%


```

set BN
accuracy <- num they got correct / number total plots that are signal 
1 - (plots they got correct)/ones that they chose
```{r}
library(dplyr)
library(stringr)

sum(setBN$`B-N-Q1` ) #should be 3, 12
setBN %>% select(`B-N-Q1`) %>% 
  mutate( points_3 = as.numeric(str_detect(`B-N-Q1`, '3')) ) %>% 
  mutate( points_12 = as.numeric(str_detect(`B-N-Q1`, '12')) ) %>% 
  mutate( acc = (points_3 + points_12)/2 ) %>% summarize(acc_tot = mean(acc)) #80

sum(setBN$`B-N-Q2` ) #should be 7, 8, 15
setBN %>% select(`B-N-Q2`) %>% 
  mutate( points_7 = as.numeric(str_detect(`B-N-Q2`, '7')) ) %>% 
  mutate( points_8 = as.numeric(str_detect(`B-N-Q2`, '8')) ) %>% 
  mutate( points_15 = as.numeric(str_detect(`B-N-Q2`, '15')) ) %>% 
  mutate( acc = (points_7 + points_8 + points_15)/3 ) %>% 
  summarize(acc_tot = mean(acc)) #82.7

sum(setBN$`B-N-Q3` ) #should be 2, 6
setBN %>% select(`B-N-Q3`) %>% 
  mutate( points_2 = as.numeric(str_detect(`B-N-Q3`, '2')) ) %>% 
  mutate( points_6 = as.numeric(str_detect(`B-N-Q3`, '6')) ) %>% 
  mutate( acc = (points_2 + points_6)/2 ) %>% summarize(acc_tot = mean(acc)) #72

#accuracy for select more than 1 
(80 + 82.7 + 72 + 68 + 67.2 + 62)/6
71.98

mutate( len = length(unlist(strsplit(`B-N-Q1`, split=","))))


#false positives
setBN %>% select(`B-N-Q1`) %>% 
  mutate( len = as.numeric(str_detect(`B-N-Q1`, ',')) + 1 ) %>%  
  mutate( points_3 = as.numeric(str_detect(`B-N-Q1`, '3')) ) %>% 
  mutate( points_12 = as.numeric(str_detect(`B-N-Q1`, '12')) ) %>% 
  mutate( false_pos = 1 - (points_3 + points_12)/len ) %>% summarize(false_pos_tot = mean(false_pos)) #0.0800

setBN %>% select(`B-N-Q2`) %>% 
  mutate( len = as.numeric(str_count(`B-N-Q2`, ',')) + 1) %>% 
  mutate( points_7 = as.numeric(str_detect(`B-N-Q2`, '7')) ) %>% 
  mutate( points_8 = as.numeric(str_detect(`B-N-Q2`, '8')) ) %>% 
  mutate( points_15 = as.numeric(str_detect(`B-N-Q2`, '15')) ) %>% 
  mutate( false_pos = 1 -  (points_7 + points_8 + points_15)/len ) %>% 
  summarize(false_pos_tot = mean(false_pos)) #0.04

setBN %>% select(`B-N-Q3`) %>% 
  mutate( len = as.numeric(str_count(`B-N-Q3`, ',')) + 1) %>% 
  mutate( points_2 = as.numeric(str_detect(`B-N-Q3`, '2')) ) %>% 
  mutate( points_6 = as.numeric(str_detect(`B-N-Q3`, '6')) ) %>% 
  mutate( false_pos = 1 -  (points_2 + points_6)/len ) %>% 
  summarize(false_pos_tot = mean(false_pos)) #0.140

#false pos rates for set B
(0.08 + 0.04 + 0.14)/3
0.0866

#false pos rates for set A
(0.08 + 0.023 +0.27)/3
0.1243
(0.0866 + 0.1243)/2
#total false positive: 10.5
```

###TOTAL RATES:
select more than 1:
false positive: 10.5%
accuracy: 71.98

accuracy for select 1: 80.5%

